A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-24 manuscript.Rmd
add missing backtick

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---

@@

We strongly suggest that you strive for respectful interactions with anyone who might want to contribute.
In fact, we hope it comes naturally to you.
To communicate that contributors can expect a welcoming and respectful environment, you can add the `r link( "https://www.contributor-covenant.org", "Contributor Covenant")` to your repository.
The Contributor Covenant is a code of conduct used by many open source project.
Contributing to an open project is daunting and a public pledge to value any contributions (even when you do not incorporate them) can help others to take the first step.

@@

@@

On your local machine, you use Git to track changes.
Online services like GitHub allow you to share these changes with others.
GitHub is not the only solution; there is also [GitLab](gitlab.com) or [BitBucket](https://bitbucket.org), which are as feature-rich as GitHub.
GitLab has the advantage that your institution can host it themselves; therefore, you are not relying on commercial service providers.
We focus on GitHub because it is the most popular service.
To upload your changes to GitHub, you need to create an account under https://github.com/join.
As a researcher, you are eligible for the `r link("https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount", "Researcher/Educator discount").
The following command creates a new GitHub repository under your GitHub account, beware this is public:
<!--Hands-on: Introduce Github-->

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output:
  bookdown::pdf_document2:
    keep_tex: true
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---

@@

We strongly suggest that you strive for respectful interactions with anyone who might want to contribute.
In fact, we hope it comes naturally to you.
To communicate that contributors can expect a welcoming and respectful environment, you can add the `r link( "https://www.contributor-covenant.org", "Contributor Covenant")` to your repository.
Contributing to an open project is daunting and a public pledge to value any contributions (even when you do not incorporate them) can help others to take the first step.
The Contributor Covenant is a code of conduct used by many open source project.

@@

However, there is some controversy around how to handle violations of a code of conduct.
For that or any other reason, you may want to adapt the Contributor Covenant, to fit the needs of you project (which you are allowed to to because it is published with a CC-BY license).

@@

On your local machine, you use Git to track changes.
Online services like GitHub allow you to share these changes with others.
GitHub is not the only solution; there is also [GitLab](gitlab.com) or [BitBucket](https://bitbucket.org), which are as feature-rich as GitHub.
GitLab has the advantage that your institution can host it themselves; therefore, you are not relying on commercial service providers.
We focus on GitHub because it is the most popular service.
To upload your changes to GitHub, you need to create an account under https://github.com/join.
As a researcher, you are eligible for the `r link("https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount", "Researcher/Educator discount")`.
The following command creates a new GitHub repository under your GitHub account, beware this is public:
<!--Hands-on: Introduce Github-->
